Containers and R---the Rockerverse and beyond

### 2020-01-16 manuscript.Rmd
formatting housekeeping

_The ordering of authors following DN as first author is alphabetical._ DN conceived the article idea, \href{https://github.com/nuest/rockerverse-paper/issues/3}{initialised the formation of the writing team}, wrote sections not mentioned below, and revised all sections.
DB wrote the section on \pkg{outsider}.
DE wrote the introduction and the section about Containerization and Rocker.
RC \& EH contributed to the section on interfaces for Docker in R.
ME contributed to the section on processing and deployment to cloud services.
CF wrote paragraphs about `r-online`, `dockerfiler`, `r-ci` and `r-db`.
BM wrote the section on research compendia and made the project Binder-ready.
HN \& JN co-wrote the section on enterprise production environments (\pkg{googleComputeEngineR}, Google Cloud Run, Kubernetes).
KR wrote the section about \pkg{wholepunch}.
NR wrote paragraphs about shared work environments and GPUs.
LS \& NT wrote the section on Bioconductor.
NX wrote the section on \pkg{liftr}.
All authors approved the final version. This articles was collaboratively written at \href{https://github.com/nuest/rockerverse-paper/}{https://github.com/nuest/rockerverse-paper/}.
The \href{https://github.com/nuest/rockerverse-paper/graphs/contributors}{contributors page}, \href{https://github.com/nuest/rockerverse-paper/commits/master}{commit history}, and \href{https://github.com/nuest/rockerverse-paper/issues/}{discussion issues} provide a detailed view on the respective contributions.

>>>>

The ordering of authors following DN as first author is alphabetical. DN conceived the article idea, \href{https://github.com/nuest/rockerverse-paper/issues/3}{initialised the formation of the writing team}, wrote sections not mentioned below, and revised all sections.
DB wrote the section on \pkg{outsider}.
DE wrote the introduction and the section about Containerization and Rocker.
RC \& EH contributed to the section on interfaces for Docker in R.
ME contributed to the section on processing and deployment to cloud services.
CF wrote paragraphs about \pkg{r-online}, \pkg{dockerfiler}, \pkg{r-ci} and \pkg{r-db}.
BM wrote the section on research compendia and made the project Binder-ready.
HN \& JN co-wrote the section on enterprise production environments (\pkg{googleComputeEngineR}, Google Cloud Run, Kubernetes).
KR wrote the section about \pkg{wholepunch}.
NR wrote paragraphs about shared work environments and GPUs.
LS \& NT wrote the section on Bioconductor.
NX wrote the section on \pkg{liftr}.
All authors approved the final version. This articles was collaboratively written at \href{https://github.com/nuest/rockerverse-paper/}{https://github.com/nuest/rockerverse-paper/}.
The \href{https://github.com/nuest/rockerverse-paper/graphs/contributors}{contributors page}, \href{https://github.com/nuest/rockerverse-paper/commits/master}{commit history}, and \href{https://github.com/nuest/rockerverse-paper/issues/}{discussion issues} provide a detailed view on the respective contributions.
